----------------------------------------TURNED PATH----------------------------------------------------------

The other option is for the ship to complete a circular turn to change directions. This can be modeled by the 
diagram below.

[Diagram]

In this path, the ship will accelerate forward (away from the earth) in a straight line for a time **deltat_1**

Using this diagram we can set up the following equation: **deltaT_T = deltat_1 + deltat_2 + deltat_3**.

As shown in the diagram, both **deltad_1** and **deltad_3** are tangent to the circle which models the turn, and pass through
the same point, being the position of the earth. As such, we can say that **deltat_1 = deltat_3** and **deltad_1 = deltad_3**.

We then get the following equation: **deltaT_T = 2deltat_1 + deltat_2**

We must solve for **deltat_2** in terms of **deltat_1** in order to get a workable equation, so we must set up the following set of 
equations:

[equations]

Using these equations we can substitute into **deltaT_T = 2deltat_1 + deltat_2** to get our final equation:

[steps]

This gives us the final equation **deltaT_T = 2deltat_1 + cancer**

It is not prossible to isolate for **deltat_1** in this equation, so we will have the computer approximate the value and calculate based
off that.

For the same reasons stated above, the time dilation over the time frame **deltat_1** is equal to the time dilation over the time frame
**deltat_3**. Given that the magnitude of velocity over the turn will be equal, we can calculate the time dilation over the time frame
**deltat_2** without summation. Thus, the simulator will only calculate the time dilation initial time step, then multiply by 2, then 
it will sum the result with the dilation over the timestep for the turn.

------------------------------------------------SIM RESULT----------------------------------------------------------
The simulator will use the above approximations for time dilation in each of the scenerios listed above to approximate the optimal
condition for each scenerio; being the trip time (the time relative to the astronaut) which yeilds an arrival within minutes of the
end of trump's presidency.

The simulator will provide the following information:
- The number of seconds between the end of trumps presidency and the arrival of the space ship.
- The trip time, the total time that the astronaut spends in the ship (relative to him)
- The total time that the astronaut spends in the ship (relative to people on earth)
- The total time skipped (the discrepency between the time the astronaut experiences and the time people on earth experience)
