\chapter{Analysis}
	\section{Proposal}
		Using special relativity we will analyze the feasibility of time travelling to the future using a variety of current and theoretical forms of transportation. Specifically, we will be exploring the possibility of using special relativity to skip to the end of Donald Trump's presidency, which is 3 years, 59 days, 20 hours, and 30 minutes from the time our ISP is due. All calculations will be done assuming we depart on our journey immediately after handing in our ISP on November 22, 2017.
		
		An idea will be considered feasible if there is a measurable difference between the time experienced by us (the one's escaping the presidency of Donald Trump) compared to the time experienced by those on earth. For example, we will even consider a one second difference a success, although a larger difference would be even better.
	\section{Ideas under consideration}
		We will carry out and present this analysis by first exploring existing technology, although most of it is not practical for our purposed. This will include methods of transportation such as biking or driving, in order to present a sense of scale for the task.
		
		We will then consider technologies that while proven on paper, and seriously considered for implementation, have not been implemented yet. This includes technologies such as Hyperloop or nuclear propulsion.

		Finally, we will look at what we can accomplish if we leave the earth. This includes ideas such as black hole starships.
	\section{Analysis approach}
		For each idea we consider, we will perform a full analysis of its ability to solve our problem. This includes considering fuel for any rockets, as well as the time needed to accelerate to what will be speeds approaching $c$. As we are only looking at the physics side of time travelling, we will ignore economic considerations such as cost or how long it would take to actually build the technology if it does not exist yet. In the case of two technologies with similar outcomes, we will only then consider economic factors. We will stage our analysis such that each technology explored improves on the weaknesses of the previous one.
